%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Courses and Skills}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Business 101, Business Law, Human Relations, Interpersonal Communication, Economics, Neuropsychology} % Role
    {Green River Coursework} % Event
    {Business Fundamentals} % Location
    {2012-2014} % Date(s)
    {Engaged in team-building exercises and presentations emphasizing active listening, game theory, and ethical business management.}

%---------------------------------------------------------
  \cventry
    {Classics, Philosophy, Sociolinguistics, Cultural Anthropology, Academic Editing, Technology and Society} % Role
    {Language and Power} % Event
    {Critical Thinking} % Location
    {Spring 2016} % Date(s)
    {Solidified critical approaches to analyzing people and ideas in a variety of fields.}

%---------------------------------------------------------
  \cventry
    {Digital Logic, Computer Architecture, Java, JVM Assembly, Discrete Math, Data Structures} % Role
    {Computer Science Foundations} % Event
    {Computer Engineering} % Location
    {2016-2017} % Date(s)
    {Learned fundamentals of problem solving and building up to complex systems using logic and object-oriented programming.}

%---------------------------------------------------------
  \cventry
    {Statistics, Python, R, Data Mining, Consumer Behavior, Ethical Data Management, Systems Thinking} % Role
    {Computing Practice and Theory: Consumer Behavior} % Event
    {Data Science Foundations} % Location
    {Spring 2017} % Date(s)
    {Learned how to collect, clean, and explore data for machine learning workflows. Evaluated positive/negative impact of Big Data in seminar.}

%---------------------------------------------------------
  \cventry
    {Linguistic Analysis, Natural Language Processing, NLTK (Python), Artificial Intelligence} % Role
    {Data and Information: Computational Linguistics} % Event
    {Natural Language Processing} % Location
    {Fall 2018} % Date(s)
    {Strengthened use of synthesis and linguistic analysis within the context of programming and studying the recent impacts of artificial intelligence.}

%---------------------------------------------------------
  \cventry
    {Computer Networking, Social Network Analysis, Systems Theory, Graph Data Structures/Algorithms/Databases} % Role
    {Student-Originated Software} % Event
    {Interdisciplinary Network Science} % Location
    {2018-2020} % Date(s)
    {Demonstrated ethics of computational kindness (reducing the cognitive load on ourselves/others) through efficient decision-making algorithms. Identified key campus partnerships between faculty, staff, and students through interviews and use of causal loop diagrams f-0or my capstone.}

%---------------------------------------------------------
\end{cventries}
