%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    { % Affiliation/role
    \begin{cvitems}
        \item {Speaker}
        \item {Deputy Speaker}
        \item {Treasurer}
      \end{cvitems}
      }
    {Geoduck Student Union} % Organization/group
    {Olympia, WA} % Location
    {Sep. 2016 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Improving both internal and external communication was top priority in keeping GSU accountable to its vision and mission.}     
        \item {Increased accessibility, streamlined agenda setting through integrating Slack and digital archiving with operations.}
         \item {Efforts created a multiplier effect: representatives found more ways to expand the capacity of the organization with their own projects.}
         \item {External stakeholders recognized GSU as an active ally with respect to their own strategic initiatives during my tenure.}
      \end{cvitems}
    }
  \cventry
    {Student Representative to the Board} % Affiliation/role
    {Evergreen Board of Trustees} % Organization/group
    {Olympia, WA} % Location
    {Sep. 2017 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Served in an advisory position on the Board, appointed by peers in student government.}
        \item {Shared updates on student groups, the work of student government, and asked for engagement from the Board.}
        \item {Actions resulted in the first joint meeting between the Board and the Student Union in the College's history.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Presidential Equity Advisor} % Affiliation/role
    {The Evergreen State College} % Organization/group
    {Olympia, WA} % Location
    {Jun. 2017 - Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Improved policies and language within the Student Code of Conduct to favor restorative justice over punitive justice.}
        \item {Collaborated with students, faculty, and staff to finalize plans for an Equity Center on campus.}
        \item {Presented recommendations on improving campus culture and climate through systems thinking.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
